---
title: "Get Started"
author: ""
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    toc: false
    number_sections: true
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message = FALSE}
library(mrgsim.ds)
library(dplyr)
```


# Load the model

Load a model using `mread_ds()` or other friends. 

```{r message = FALSE}
mod <- mread_ds("popex-2.mod", outvars = "IPRED, DV, ECL")
```


This model is almost identical to the same model loaded with `mread()`; there 
is just some extra information included to make sure it works well with the 
`mrgsim.ds` approach. 

# Simulate

To simulate, call `mrgsim_ds()`

```{r}
data <- evd_expand(amt = c(100, 300, 700), ii = 24, addl = 4, ID = 1:10)

set.seed(98)
out <- mrgsim_ds(mod, data = data)
```

The output handles very similar to regular `mrgsim()` output

```{r, fig.width = 7, fig.height = 4}
out

head(out)

dim(out)

plot(out, nid = 10)
```

# Simulation files

Simulation files are always initially stored in `tempdir()` 

```{r, echo = FALSE, message = FALSE}
purge_temp()
```


```{r}
out <- lapply(1:10, \(x) mrgsim_ds(mod, data)) %>% reduce_ds()

list_temp()
```

To save outputs to a persistent location, use `write_ds()`.

```{r, echo = FALSE}
save_dir <- tempdir()
```


```{r, warning = FALSE, message = FALSE}
save_ds(out, file = file.path(save_dir, "sims.rds"))
```

This creates an `.rds` file holding the (very lightweight) simulation output object _and_ it 
relocates all the backing files to `save_dir`. 

To read the simulations back into R

```{r}
bah <- read_ds(file.path(save_dir, "sims.rds"))

bah
```

An alternative is to rename and move. 

```{r}
rename_ds(bah, "regimen-1")
move_ds(bah, save_dir)
```
